\documentclass[11pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}

\begin{document}

\begin{center}
    {\LARGE \textbf{Jane Doe}}\\
    \vspace{2mm}
    Email: jane.doe@example.com \\
    Phone: +1 234 567 8901 \\
    LinkedIn: \href{https://linkedin.com/in/janedoe}{linkedin.com/in/janedoe} \\
    GitHub: \href{https://github.com/janedoe}{github.com/janedoe}
\end{center}

\section*{Professional Summary}
Mid-level Data Scientist with 3+ years of experience in machine learning, data analysis, and business intelligence. Skilled in Python, SQL, and statistical modeling to drive actionable insights.

\section*{Education}
\textbf{M.Sc. in Data Science}, ABC University \hfill 2020 -- 2022 \\
GPA: 3.9/4.0

\textbf{B.Sc. in Computer Science}, XYZ University \hfill 2016 -- 2020 \\
GPA: 3.8/4.0

\section*{Experience}

\textbf{Data Scientist}, TechCorp Inc. \hfill Jun 2022 -- Present
\begin{itemize}[noitemsep]
    \item Developed predictive models for customer churn, increasing retention by 15\%.
    \item Built ETL pipelines to process large datasets from multiple sources.
    \item Created interactive dashboards with Power BI and Plotly.
\end{itemize}

\textbf{Data Analyst}, DataSolutions Ltd. \hfill Jul 2020 -- May 2022
\begin{itemize}[noitemsep]
    \item Conducted statistical analysis on sales and marketing data.
    \item Automated reporting using Python and SQL, saving 10+ hours per week.
    \item Collaborated with engineering team to improve data quality and pipelines.
\end{itemize}

\section*{Skills}
\begin{itemize}[noitemsep]
    \item \textbf{Programming:} Python, R, SQL, Bash
    \item \textbf{ML / AI:} scikit-learn, TensorFlow, XGBoost
    \item \textbf{Visualization:} Matplotlib, Seaborn, Plotly, Power BI
    \item \textbf{Databases:} PostgreSQL, MySQL, MongoDB
    \item \textbf{Other:} Git, Docker, Airflow, Agile methodology
\end{itemize}

\section*{Projects}
\textbf{Customer Segmentation using Clustering} \hfill 2022 \\
Analyzed 100k+ customer records to identify 5 key segments. Improved targeted marketing strategy.

\textbf{Sales Forecasting Model} \hfill 2021 \\
Developed ARIMA and XGBoost models to predict sales, reducing inventory costs by 12\%.

\end{document}
